Assessing Tor's Usability as a Censorship Circumvention Tool

### 2015-05-12 cs261n-paper/paper.tex
added and formatted quotes for ux results

>>>>

{\color {red}

We saw an SEO poisoning opportunity.

\begin{quote}{\it
`` I'm going to use Chrome, because that's what I use at home...
I'm just going to open it up, and I'm going to type in "download tor" because 
that's what I'm supposed to do. And I'm going to click on the first one, because,
at the top, which is `Download Tor'.''} -P
\end{quote}

\begin{quote}{\it
``Okay. So I just would type in `tor' in the uh search engine and `Tor Project'...
`Anonymity Online'... I guess this is it. And I click. And the there is a "Download Tor", 
so I am going to click this.''} -P2
\end{quote}

\begin{quote}{\it
``There's, like, the first thing on the page is called the Tor Project, and I wouldn't figure out what that is,
but then it says `Tor Browser' just a little bit underneath, so I get, I put two and two together and I figure 
this is probably what I have to download.'}' -P3
\end{quote}

\begin{quote}{\it
``so I am going to type in `tor mac download.'
And that gives me some suggestions. I pick the first one.'''} -P4
\end{quote}

\begin{quote}{\it
``I am going to go to torproject.org... I am seeing the second result is `Download Tor.'
That might save a few steps, I will click on that.''} -P5
\end{quote}

Something unexpected which interfered with Tor's usability is that Mac's usable 
security feature which prevents opening unsigned code made Tor much less usable.

\begin{quote}{\it
`` `The app has been modified...', blah blah blah... Oh, this is annoying. I would maybe normally stop now.''} -P1
\end{quote}

\begin{quote}{\it
`` `TorBrowser' can't be opened because it's from an unidentified developer.'
Grr! I express some frustration at this fact.''} - P4
\end{quote}

Lessons learned: 
Leverage visuals and interface design to prioritize communication to users. Most of the 
important information was communicated with paragraphs of text that users actively 
communicated that they did not read or did not want to read and only read because of 
issues they were experiencing.

\begin{quote}{\it
``...it looks like I should click there, because it is purple. No, not because it's purple, but... 
[laughter] because it has that little cloud with the arrow... and you can't click anywhere else to download.''} -P1 
\end{quote}

\begin{quote}{\it
``There's this big purple icon on the left side of the screen that says `Download Tor Browser',
so I'm going to click on that because it seems like the most obvious thing.
There are a couple of other small words on the screen that I'm not going to look at, because this seems like the most obvious thing to do.''} -P3
\end{quote}

\begin{quote}{\it
"Don't open documents downloaded through Tor... That doesn't make sense to me.
But I'll just pay attention because it's in capitals and it's like they're yelling at me.''} -P1
\end{quote}

Most participants did not have any interest or comprehension for advanced features.
In usability literature, it is good to just configure these for users, but Tor does not track
information on users. Maybe it's good to have failsafe defaults and less options.

\begin{quote}{\it
``Yeah, and like the settings of your Tor Browser, I guess.''} -P1
\end{quote}

\begin{quote}{\it
``But then I have toyed around before with like preferences and looking around and 
usually it's out of my understanding.''} -P5
\end{quote}

\begin{quote}{\it
``So yeah, there was an onion. Small green onion. And yeah, I guess, it's new identity.
So I'm guessing it's the same thing as with Google, when you open a page and you don't 
want the history to show up or something. And then you can, it's like you're disconnected 
from your Gmail account and everything, you can type that as a different user.''} -P3 
\end{quote}
}
